Appendix S4. The relative importance of evolution in populations and communities

### 2024-11-03 manuscript/Appendix_S4_v01.Rmd
began mc sim analysis

m.2.hmsc = Hmsc(Y = Y, XData = XData, XFormula = ~E+Esq+dx1, studyDesign = studyDesign, ranLevels = list(sample = rL))
# Bayesian model parameters
nChains <- 2
thin <- 5
samples <- 2000
transient <- 1000*thin
verbose <- 500*thin
# sample MCMC
m.2.sample <- sampleMcmc(m.2.hmsc,thin=thin,sample=samples,transient=transient,nChains=nChains,verbose=verbose)
m2.post.hmsc <- convertToCodaObject(m.2.sample)
```

>>>>

m.2.hmsc = Hmsc(Y = Y, XData = XData, XFormula = ~E+Esq+dx1, studyDesign = studyDesign, ranLevels = list(sample = rL))
# Bayesian model parameters
nChains <- 2
thin <- 5
samples <- 2000
transient <- 1000*thin
verbose <- 500*thin
# sample MCMC
m.2.sample <- sampleMcmc(m.2.hmsc,thin=thin,sample=samples,transient=transient,nChains=nChains,verbose=verbose)
m2.post.hmsc <- convertToCodaObject(m.2.sample)
```
```{r}
m2.post.hmsc <- convertToCodaObject(m.2.sample)
summary(m2.post.hmsc$Beta)
bayesplot::mcmc_trace(m2.post.hmsc$Beta)
bayesplot::mcmc_areas(m2.post.hmsc$Beta,area_method = c("equal height"))
```

```{r}
Gradient <- constructGradient(m.2.sample,focalVariable="dx1",non.focalVariables=list(E=list(2),Esq=list(2)),ngrid=59)
# Esq is manually constructed as gradient-produced E^2
Gradient$XDataNew$Esq <- Gradient$XDataNew$E^2
predY <- predict(m.2.sample,XData=Gradient$XDataNew,expected=TRUE)
plotGradient(m.2.sample,Gradient,pred=predY,showData=T,measure="Y",main="",xlab="dx1_t",ylab="predicted N_t+1")
```
